Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/experiments.tex
Updating spacing on figures in the experiments section
inset for circuit plot
lots of plot changes

\begin{figure}
{\footnotesize
\begin{tabular}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & QDR \\
\end{tabular}
}
\caption{System configurations used for the experiments. \label{fig:systems}}
\end{figure}

@@

We evaluate the efficiency and scalability of Legion using
three applications on three clusters (see Figure~\ref{fig:systems}).
For each application, multiple problem sizes were used, and each size problem was
run on subsets of each machine ranging from the smallest (a single CPU core or GPU)
to the largest or near-largest (except Keeneland, where we limited
runs to 32 nodes to get sufficient cluster time).
By examining performance of the same size problem over progressively larger
machines, we measure Legion's strong scaling.
By increasing the problem size as well, we also measure weak scaling.

@@

The circuit simulation has a simple application-specific mapper.  At initialization
time, the mapper queries the list of GPUs in the machine and identifies each GPU's
framebuffer memory and {\em zero-copy} memory (pinned memory that both the GPU and
CPUs in the system can access directly).  Once the circuit is partitioned, the partitions
are assigned a home GPU in round-robin fashion.  Every task related to that partition is
then sent to the home GPU, with no task stealing allowed.  
%
% FIXME CUT
% We could put this nice sentence back in if we have space.
%
%(In a well-partitioned circuit,
%load imbalance is low enough that the cost of moving the private data for a piece from one
%GPU to another outweighs any benefits.)
%
% FIXME CUT  
% If we find enough space this sentence and the figure can be reinserted here.
%  The regions for a task are mapped as 
%shown in Figure~\ref{fig:gpumapping}.

@@

\begin{figure}
\subfigure[Circuit simulation speed relative to single-GPU implementation.]
{
\includegraphics[scale=0.4]{figs/circuit_speedups.pdf}
\makebox[0pt][r]{
\raisebox{0.25 in}{
\includegraphics[scale=0.18]{figs/circuit_speedups_zoom.pdf}
}
}
\label{fig:ckt_speed}
}

\subfigure[Overhead of circuit simulation on Keeneland with 3 GPUs/node.]
{
\includegraphics[scale=0.4]{figs/circuit_overhead.pdf}
\label{fig:ckt_overhead}
}
\caption{Circuit simulation results.}
\end{figure}

@@

%\subfigure[Effect of load-balanced partitioning.]
%{
%\includegraphics[scale=0.4]{figs/fluid_balance.pdf}
%\label{fig:fluid_balance}
%}
\caption{Fluid simulation results.}
\end{figure}

@@

\subfigure[Keeneland results.]
{
\includegraphics[scale=0.4]{figs/Keeneland_amr.pdf}
\label{fig:amr_keeneland}
}
\caption{Throuphput of adaptive mesh refinement in millions of cells/s \label{fig:amr_total}}
\end{figure}

>>>>

\begin{figure}
{\footnotesize
\begin{tabular}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & QDR \\
\end{tabular}
}
\vspace{-2mm}
\caption{System configurations used for the experiments. \label{fig:systems}}
\vspace{-6mm}
\end{figure}

@@

We evaluate the efficiency and scalability of Legion using
three applications on three clusters (see Figure~\ref{fig:systems}).  All three
clusters were Linux-based, and the Legion runtime was built using pthreads for
managing CPU threads, CUDA\cite{cuda} for GPUs, and GASNet\cite{GASNET07} for
inter-node communication.  The RDMA features of GASNet were used to create a 
globally addressable, but relatively slow, ``GASNet memory'' that is accessible
by all nodes.
For each application, multiple problem sizes were used, and each size problem was
run on subsets of each machine ranging from the smallest (a single CPU core or GPU)
to the largest or near-largest (except Keeneland, where we limited
runs to 32 nodes to get sufficient cluster time).
By examining performance of the same size problem over progressively larger
machines, we measure Legion's strong scaling.
By increasing the problem size as well, we also measure weak scaling.

@@

The circuit simulation has a simple application-specific mapper.  At initialization
time, the mapper queries the list of GPUs in the machine and identifies each GPU's
framebuffer memory and {\em zero-copy} memory (pinned memory that both the GPU and
CPUs in the system can access directly).  Once the circuit is partitioned, the partitions
are assigned a home GPU in round-robin fashion.  Every task related to that partition is
then sent to the home GPU, with no task stealing allowed.  
%
% FIXME CUT
% We could put this nice sentence back in if we have space.
%
(In a well-partitioned circuit,
load imbalance is low enough that the cost of moving the private data for a piece from one
GPU to another outweighs any benefits.)
%
% FIXME CUT  
% If we find enough space this sentence and the figure can be reinserted here.
  The regions for a task are mapped as 
shown in Figure~\ref{fig:gpumapping}.

\begin{figure}
\includegraphics[scale=0.48]{figs/CircuitMem.pdf}
\caption{Tasks and data for the circuit simulation on a cluster of GPUs.}
\label{fig:gpumapping}
\end{figure}

@@

\begin{figure}
\subfigure[Circuit simulation speed relative to single-GPU implementation.]
{
\includegraphics[scale=0.4]{figs/circuit_speedups.pdf}
\makebox[0pt][r]{
\raisebox{0.25 in}{
\includegraphics[scale=0.4]{figs/circuit_speedups_zoom.pdf}
}
}
\label{fig:ckt_speed}
}

\subfigure[Overhead of circuit simulation on Keeneland with 3 GPUs/node.]
{
\includegraphics[scale=0.4]{figs/circuit_overhead.pdf}
\label{fig:ckt_overhead}
}
\vspace{-2mm}
\caption{Circuit simulation results.}
\vspace{-6mm}
\end{figure}

@@

%\subfigure[Effect of load-balanced partitioning.]
%{
%\includegraphics[scale=0.4]{figs/fluid_balance.pdf}
%\label{fig:fluid_balance}
%}
\vspace{-2mm}
\caption{Fluid simulation results.}
\vspace{-6mm}
\end{figure}

@@

\subfigure[Keeneland results.]
{
\includegraphics[scale=0.4]{figs/Keeneland_amr.pdf}
\label{fig:amr_keeneland}
}
\vspace{-2mm}
\caption{Throughput of adaptive mesh refinement code. \label{fig:amr_total}}
\vspace{-6mm}
\end{figure}
